smooth-sea

### 2018-05-17 index.rmd
progress on modeling, setting up format and basic data for site

---
title: "smooth-sea"
author: "Chris Hess"
date: "May 17, 2018"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "hesscl.com", href: "http://hesscl.com", align: right }
    orientation: columns
    theme: bootstrap
    logo: logo.svg
    source_code: "https://github.com/hesscl/smooth-sea"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: "smooth-sea"
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "hesscl.com", href: "http://hesscl.com", align: right }
    orientation: columns
    theme: bootstrap
    logo: logo.svg
    source_code: "https://github.com/hesscl/smooth-sea"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#source("./smoothSpatiotemporal.R", echo = FALSE)
```

Home {data-icon="fa-home"}
=====================================

Column
-------------------------------------

### Welcome!

This website provides information for the paper _Estimating Neighborhood Asking Rents using Scraped Craigslist Rental Listings_

You can download the R source code and data for this project from Github [here](https://github.com/hesscl/smooth-sea)

Contact Chris Hess at [hesscl@uw.edu](mailto://hesscl@uw.edu) for more information about this report.

_This page was last updated: `r Sys.Date()`_
